Predicting Internet Path Dynamics and Performance with Machine Leanring

### 2017-12-10 paper-tex/paper.tex
minor in paper, many things to do
We'd better start writing the report now

\usepackage{booktabs} % For formal tables

@@

\begin{abstract}
TODO
\end{abstract}

@@

TODO

\section{Related Works}
TODO
\subsection{Type Changes and {\itshape Special} Characters}
You can indicate italicized words or phrases in your text with the command \texttt{{\char'134}textit}; emboldening with the command \texttt{{\char'134}textbf} and typewriter-style (for instance, for computer code) with \texttt{{\char'134}texttt}.  
\subsection{Math Equations}
You may want to display math equations in three distinct styles:
inline, numbered or non-numbered display.  Each of
the three are discussed in the next sections.

>>>>

\usepackage{booktabs} % For formal tables
\usepackage{url}

@@

\begin{abstract}
We study the problem of predicting internet path dynamics and performance. We use \texttt{traceroute} measurement and machine learning models.
\end{abstract}

@@

TODO 
\section{Related Works}
TODO
